### 2016-03-10 paper/stereo.tex

\section{Swarm Fusion implementations} \yasu{this section is very rough
at the moment. requires polishing. but algorithms might change as we run
experiments.}
We now explain detailed implementation of the Swarm Fusion method for
three problems in Computer Vision.

\subsection{Swarm Fusion stereo}
We start with a relatively ``easy'' problem, a depthmap stereo problem
with unary and submodular pairwise terms.
%
We use Middlebury stereo datasets for the experiments. Unary terms are
computed as the average Normalized Cross Correlation score between the
reference image and the others inside a $7\times 7$ pixels
window. Pairwise terms are simple Pottz model. Unary terms are rescaled
by a factor of \yasu{X value?} to define the total energy.

>>>>

\section{Swarm Fusion implementations}
We compare our Swarm fusion methods against competing approaches over three
problems in Computer Vision. The SF architecture has high degrees of
freedom and the challenge is to properly quantity the contribution of
various algorithmic aspects. For this purpose, we carefully design the
SF architecture for each problem independently, sometimes limiting the
capabilities on purpose, to enable effective and fair comparative evaluation.
We now explain the details of the three problems.

% We pick three representative problems in Computer Vision to evaluate the
% effectiveness of the Fusion swarm methods against existing methods. We
% control the SF architectures for each problem independently to make
% compa
%
%\yasu{this section is very rough at the moment. requires polishing. but
%algorithms might change as we run experiments.}  We now explain detailed
%implementation of the Swarm Fusion method for three problems in Computer
%Vision (See Fig.~\ref{fig:problem}).  5
\begin{figure}[tb]
 \includegraphics[width=\columnwidth]{figure/problem.pdf} \caption{We
 compare our Swarm Fusion methods against various baselines on a
 depthmap stereo~\cite{middle_bury_stereo}, an optical
 flow~\cite{middlebury_optical_flow}, or a layered depthmap
 estimation~\cite{layered_depthmap} problem.  }\label{fig:problem}
\end{figure}

\subsection{Swarm Fusion stereo}
We start with a simple depthmap stereo problem with standard unary and
submodular pairwise terms. Unary terms are computed as the average
Normalized Cross Correlation score between the reference image and the
others inside a $7\times 7$ pixels window. Pairwise terms are simple
Pottz model. The total energy is defined by the sum of the two, while
the pairwise term is scaled by a factor of \yasu{X value}.
%
We use Middlebury stereo datasets for the experiments.
